Renewal and stability in populations structured by remaining years of life

### 2016-05-20 ThanoRepro/ThanoRepro.tex
minor edits from some weeks ago

\subsection*{Results}
In stability, the years lived and left renewal models are
commensurable, implying identical intrinsic growth rates.
I demonstrate approximate symmetry between years lived and left age structure in
stability when subject to intrinsic growth rates equal magnitude and opposite sign.

@@

\subsection*{Contribution}
The years left renewal model offers a new perspective on population renewal,
and it is valid more generally as an aspect of birth-death processes.
\vspace{2cm}

>>>>

\subsection*{Results}
In stability, the years lived and left renewal models are
commensurable, implying identical intrinsic growth rates.
I demonstrate approximate symmetry between years lived and left age structure in
stability when subject to intrinsic growth rates of equal magnitude and opposite
sign.

@@

\subsection*{Contribution}
The years-left renewal model offers a new perspective on population renewal.
\vspace{2cm}
